%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection[page1sidebar]{Recent Work Experience}


\cvexperience{Chief Technology Officer}{Evoluzione Blockchain Internazionale}{Jan 2021 -- Oct 2021}{Lima - Peru}
\begin{itemize}
    \item Responsible of establishing and promoting the technological strategy and the architectural direction.
    \item Leader of the Peru Token Project: First Blockchain Wallet in Peru.
    \item Leader of the Blockchain Certification Project. Traceability, validation and verification of documents. Stack: Algornad Protocol, API Purestake, AWS Infraestructure, Node.js, PostgreSQL, Angular, IPFS.
    \item Develop the structure for the application for funding requirements to the Algorand Foundation for the blockchain certification project.
    \item Outline work plans, determine results, write timelines and generate initial budget as part of project scope determination.
    \item Negotiate key deals with vendors and suppliers.
    \item Achieve exclusive strategic alliances with key technology partners.
    \item Meeting with customers to gain a better understanding of the business needs and collaboratively define the best solutions.
    \item Compile and analyze metrics to measure team´s performance and provide an accurate estimate on the expected delivery of features and products.
    \item Initiated and coordinated the implementation of new data security measures across the company’s IT infrastructure.
    \item Definition of data architecture for the products to be released.
\end{itemize}

\divider

\cvexperience{Project Manager}{Círculo de Crédito}{Jan 2018 -- Jan 2021}{Lima - Peru}
\begin{itemize}
    \item Responsible of planning, management and delivery of software development and IT-related projects.
    \item Build high-performance teams that are highly engaged and productive, using agile methods, skills, tools and practices to ensure that the project generates successful outcomes.
    \item Lead all aspects of backlog grooming, triage and prioritization, and cross-functonal coordination.
    \item Responsible for defining the scope of development for new product features ongoing feature improvements including management of all backlog and project management activities.
    \item Establish and maintain a high level of credibility with internal and external partners.
    \item Analytical ability to break down complex problems and efficiently use data and analytics to align project goals.
    \item Track progress, assess risks, coordinate delivery, and actively communicate conধngency and miধgaধon plans for the team.
    \item Preparation of technical-functional proposal.
    \item Leadership of the first Mobile App strategic project of the organizaধon
    \item Migration on-premise IT infrastructure to Cloud AWS
    \item Implementation of Integration Projects with Financial Entities using
    \item APIs and Web Services: BFP, BanBif, Cencosud, Entel.
    \item Extensive knowledge of the data sources such as RCC, Sunat, Afp, Debts reported, Commercial late payment, Customs, Microfinance and internal sources.
    \item Design and development of information analysis tools for Units and Managements
    \item Analyze the existing information generation processes and design improvement proposals, seeking the centralization and optimization of repetitive processes.
    \item Data enrichment and cleansing.
    \item Massive data processing for prospecting and data enrichment models.
\end{itemize}

\divider

\cvexperience{Software Architect}{Xchange Perú}{Jan 2016 -- Dec 2017}{Lima - Peru}
\begin{itemize}
    \item Responsible for the definition of the software and data architecture.
    \item Migration on-premise IT infrastructure to Cloud AWS
    \item Development and integration through REST services WCF, JSON, SQL Server 2008 R2
    \item Design and development of information analysis tools for Units and Managements
    \item Analyze the existing information generation processes and design improvement proposals, seeking the centralization and optimization of repetitive processes.
    \item Data enrichment and cleansing.
    \item Massive data processing for prospecting and data enrichment models with the RCC data.
    \item Design and program ETL for process optimization: Kettle Pentaho Data Integration.
    \item Web scraping to get 2MM people base. SSIS technology, C\#, SQL Server 2008.
    \item IIS 7.0 Management and Administration
    \item Deployment of Web Applications on IIS Server
    \item Web applications development. Frontend and backend: HTML, CSS, Javascript, C\#, MVC, ASP.Net Web forms, SQL Server
    \item MDX queries to extract data from OLAP cubes.
\end{itemize}

\divider

\cvexperience{Database Administrator}{Xchange Perú}{Apr 2015 -- Dec 2015}{Lima - Peru}
\begin{itemize}
    \item Management and monitoring of the company's technological infrastructure.
    \item Installation, configuration and database management of new environments.
    \item Manage access to production servers according to established policies.
    \item Perform installation of database services such as Reporting Services, Integration Services, drivers and configure them for the consumption of Core Applications.
    \item Provide support in user incidents according to the corresponding level according to the established SLA.
    \item Administration of backups and restores.
    \item Guarantee the security of the databases: availability, integrity and confidentiality.
    \item Manage maintenance plans for non-productive and productive databases.
    \item Database monitoring (queries, process id, traces, anomalous activities and others)
    \item Data Replication between Servers.
    \item DB Object Structure Optimization. Tables, Indices, Store Procedures, Functions.
    \item Maintenance of Partitions and Logs of the DB.
    \item OLAP Cubes Information Update.
    \item OLAP Cubes Backup.
\end{itemize}

\divider

\cvexperience{System Analist}{Xchange Perú}{Sep 2010 -- Mar 2015}{Lima - Peru}
\begin{itemize}
    \item ETL Process Design and Automation with Pentaho Data Integration.
    \item Design, Optimization and Automation of DB SQL 2005 and 2008.
    \item Implementation of Search Engines and Data Extraction Processes.
    \item Maintenance and updating of new functionalities of Web applications: C\#, ASP.Net
    \item Maintenance and updating of Web services: SOAP XML
\end{itemize}

\divider

\cvexperience{System Analist}{Cooperativa de Ahorro y Crédito Finantel}{Sep 2008 -- Aug 2010}{Lima - Peru}
\begin{itemize}
    \item Responsible for ensuring that the quality of the development of Information Systems and compliance with functional requirements.
    \item Responsible for defining the development methodology to carry out the functional analysis, design, construction and maintenance of the information systems.
    \item Database analysis and design.
    \item Maintenance of the company’s Back Office (Web and Client Server).
    \item Management of the Business Core, giving support to users and resolution of incidents.
    \item Advanced queries, store procedures, tuning and management DB
\end{itemize}
